Project Codebook
==================
Data Source
----------
Downloaded at https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip. The line of code is included in run_analysis.R and run_analysis.Rmd files

Data Cleaning
----------------
The original data have 561 varibles and are separated into two data sets:
 1. Training set: 7352 observations
 2. Test set: 2947 observations

The following steps are taken to reformat the data:
 1. Combine training and test data sets with one added column to label the source.
 2. Extract only the mean and standard deviation. This reduces the number of varibles to 66.
 3. Label the activities using the following:
   * WALKING
   * WALKING_UPSTAIRS
   * WALKING_DOWNSTAIRS
   * SITTING
   * STANDING
   * LAYING
 4. A new tidy data set has been created by aggregating the mean of each variable for each subject and activity.

For more detailed implementation, please refer to **run_analysis.Rmd**.

Overview of the Processed Data:
-----------------
Structure:
```{r, echo = F}
str(dt.tidy)
```

Summary:
```{r, echo = F}
summary(dt.tidy)
```